Python como Entorno Científico de Desarrollo

### 2008-07-05 clases/imath_julio_2008/seminario_python2.tex
Unas pequeñas correcciones para que esto compile y listo
Solo sincronizando

\begin{frame}
  \frametitle{Ejercicio}

@@

\begin{frame}
  \frametitle{Profiling}
\defverbatim[colored]\testcode{
\begin{lstlisting}
$ python -m profile main.py
         101006 function calls (96090 primitive calls) in 1.740 CPU seconds

@@

   ncalls  tottime  percall  cumtime  percall filename:lineno(function)
        1    0.000    0.000    0.000    0.000 :0(__import__)
        2    0.000    0.000    0.000    0.000 :0(__new__)
       15    0.000    0.000    0.000    0.000 :0(_getframe)
      589    0.000    0.000    0.000    0.000 :0(abs)
       38    0.000    0.000    0.000    0.000 :0(acquire_lock)
      144    0.000    0.000    0.000    0.000 :0(add_docstring)
        2    0.000    0.000    0.000    0.000 :0(allocate_lock)
\end{lstlisting}
}  
\end{frame}

@@

>>>>

@@

\defverbatim[colored]\testcode{
\begin{lstlisting}
$ python -m profile main.py
         101006 function calls (96090 primitive calls) in 1.740 CPU seconds

@@

   ncalls  tottime  percall  cumtime  percall filename:lineno(function)
        1    0.000    0.000    0.000    0.000 :0(__import__)
        2    0.000    0.000    0.000    0.000 :0(__new__)
       15    0.000    0.000    0.000    0.000 :0(_getframe)
      589    0.000    0.000    0.000    0.000 :0(abs)
       38    0.000    0.000    0.000    0.000 :0(acquire_lock)
      144    0.000    0.000    0.000    0.000 :0(add_docstring)
        2    0.000    0.000    0.000    0.000 :0(allocate_lock)
\end{lstlisting}
}
\begin{frame}
  \frametitle{Profiling}
 \testcode 
\end{frame}

@@

\defverbatim[colored]\testcode{
\begin{lstlisting}
from ctypes import c_int, POINTER #1
import numpy as np
from numpy.ctypeslib import load_library,ndpointer #1

def dgesv(N,A,B):
    A = np.asfortranarray(A.astype(np.float64)) #2
    B = np.asfortranarray(B.astype(np.float64))

    cN=c_int(N)
    NRHS=c_int(1)
    LDA=c_int(N)
    IPIV=(c_int * N)()
    LDB=c_int(N)
    INFO=c_int(1)

    lapack=load_library('liblapack.so','/usr/lib/')#3
\end{lstlisting}
}
\begin{frame}
  \frametitle{ctypes}
  \testcode
\end{frame}

\defverbatim[colored]\testcode{
\begin{lstlisting}
     lapack.dgesv_.argtypes=[POINTER(c_int),
             POINTER(c_int),
             ndpointer(dtype=np.float64,
             ndim=2,
             flags='FORTRAN'),
             POINTER(c_int), POINTER(c_int),
             ndpointer(dtype=np.float64,
                       ndim=2,
                       flags='FORTRAN'),
             POINTER(c_int),POINTER(c_int)]#4

    lapack.dgesv_(cN,NRHS,A,LDA,IPIV,B,LDB,INFO)#5
    return B

print dgesv(2,np.array([[1,2],[1,4]]),np.array([[1,3]]))
\end{lstlisting}
}
\begin{frame}
  \testcode
\end{frame}
